Liquid Amortization: Proving Amortized Complexity with LiquidHaskell (Functional Pearl)

### 2024-07-18 paper/main.tex
Fix last typesetting issues

-- simplify using monotonicity of log2
  ? log2Mono (2 * max n 2) (4 + 2 * n1 + 2 * n2)
  =<= log2 (4 + 2 * n1 + 2 * n2) + 14
  ? log2Mono (4 + 2 * n1 + 2 * n2) (4 + n1' + n2')
  =<= log2 (4 + n1' + n2') + 14
  ? log2Mono (4 + n1' + n2')
    (max (length (toList u1
      ++ tuplesToList (seqToList q1) ++ toList v1
    ) + length (toList u2
      ++ tuplesToList (seqToList q2) ++ toList v2
    )) 2)
  =<= log2 (max (length (toList u1
      ++ tuplesToList (seqToList q1) ++ toList v1)
    + length (toList u2
      ++ tuplesToList (seqToList q2) ++ toList v2)
    ) 2) + 14
  === log2 (max (length (seqToList qq1)
    + length (seqToList qq2)) 2) + 14
  *** QED
  where
    n1 = length (seqToList q1)
    n2 = length (seqToList q2)
    n = n1 + n2
    n1' = length (tuplesToList (seqToList q1))
    n2' = length (tuplesToList (seqToList q2))
\end{lstlisting}

@@

>>>>

-- simplify using monotonicity of log2
  ? log2Mono (2 * max n 2) (4 + 2 * n1 + 2 * n2)
  =<= log2 (4 + 2 * n1 + 2 * n2) + 14
  ? log2Mono (4 + 2 * n1 + 2 * n2) (4 + m1 + m2)
  =<= log2 (4 + m1 + m2) + 14
  ? log2Mono (4 + m1 + m2)
    (max (length (toList u1
      ++ tuplesToList (seqToList q1) ++ toList v1
    ) + length (toList u2
      ++ tuplesToList (seqToList q2) ++ toList v2
    )) 2)
  =<= log2 (max (length (toList u1
      ++ tuplesToList (seqToList q1) ++ toList v1
    ) + length (toList u2
      ++ tuplesToList (seqToList q2) ++ toList v2
    )) 2) + 14
  === log2 (max (length (seqToList qq1)
    + length (seqToList qq2)) 2) + 14
  *** QED
  where
    n1 = length (seqToList q1)
    n2 = length (seqToList q2)
    n = n1 + n2
    m1 = length (tuplesToList (seqToList q1))
    m2 = length (tuplesToList (seqToList q2))
\end{lstlisting}

@@

\balance
